\documentclass[12pt]{report}

\usepackage{subfigure}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{minted}
\usepackage{graphicx}
\usepackage{float}
\usepackage{pgfgantt}   
\usepackage{lipsum}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{setspace}
\PassOptionsToPackage{hyphens}{url}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=3cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=black]{hyperref}

\begin{document}
\input{title/title.tex}
\onehalfspacing
\setlength{\parskip}{1em}
\begin{abstract}
Robot motion planning based on computer vision is an essential topic in the field of AI. While the majority applications allow for relatively high manipulation tolerance, such as pick and place. 

In this project, I address the precise AI planning and control problem of putting shoelaces on a marked shoe using a bimanual robot, ABB YuMi, and an external camera. Starting with one arm holding one end of the lace, YuMi can adjust the orientation of the shoe if necessary, then pass the shoelace through the shoe hole. As an extension, YuMi will also plan sequences of trajectories for completing more holes up to finishing the whole shoe.

The main emphasis of this project is on computing the precise 6D pose of the shoe hole to estimate the approaching posture of YuMi’s arm accordingly. The final approach to tackle this problem is by combining random sample consensus (RANSAC) technique and some pre-defined constraints. Other topics, including dual arm motion planning, object detection and localization, and accurate offset adjustment, are also covered. Every single function, as well as the integrated system, is then experimented and evaluated.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
% It is usual to thank those individuals who have provided particularly useful assistance, technical or otherwise, during your project. 
\begin{abstract}
I would like to firstly express my sincere gratitude to my supervisor Prof Yiannis Demiris for his helpful advice, constructive feedback, and continuous support throughout the course of my project.

Furthermore, I would like to thank all the members in the Personal Robotics Lab, in particular, Urbano Miguel Nunes and Rodrigo Chacon Quesada, for their practical tips and friendliness, which kept me going whenever I was faced with a problem.

Also, I would like to thank my friends around the world, who always bring me happiness and encouragement as well as the wine we drank, the scenery we saw and the things we went through together.

Finally, I would like to thank my family, for their unconditional support since I was born and giving me the opportunity to study at Imperial College.
%Thanks mum, dad, my family!

%Thanks my supervisor, friends, PhDs in Lab and YuMi!

%Thanks breakfast, lunch, and dinner!

%Thanks gym, sunshine, coffee, movies, and London!

%Finally, thanks my brain!
\end{abstract}


\setlength{\parskip}{0em}
\tableofcontents
\newpage

%\listoffigures
%\listoftables
\setlength{\parskip}{0.7em}
\input{introduction/introduction.tex}
\input{background/background.tex}
\input{RequirementsCap/requirementscap.tex}
\input{AnalysisDesign/analysisdesign.tex}
\input{Implementation/implement_cv.tex}
\input{Implementation/implement_mp.tex}
\input{TaR/tar.tex}
\input{conclusion/conclusion.tex}
\input{Futurework/future.tex}
\input{UserGuide/userguide.tex}


\bibliographystyle{plainnat}
\bibliography{bibs/sample}
\input{appendix/figtab.tex}

\end{document}